---
title: "README"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
#Downloading data if not exists
if(!file.exists(file="summarySCC_PM25.rds")||
   !file.exists(file="Source_Classification_Code.rds")){
  download.file(url = "https://d396qusza40orc.cloudfront.net/exdata%2Fdata%2FNEI_data.zip",
                destfile = "data.zip")
  unzip("data.zip")
}
#Reading data
NEI <- readRDS("summarySCC_PM25.rds")
SCC <- readRDS("Source_Classification_Code.rds")
#Have total emissions from PM2.5 decreased in the United States
#from 1999 to 2008? Using the base plotting system, make a plot
#showing the total PM2.5 emission from all sources for each 
#of the years 1999, 2002, 2005, and 2008.
p1 <- tapply(NEI$Emissions, NEI$year, sum)
#Creating plot
plot(p1,x = names(p1),type = "l",main = "total PM2.5 emission",
     ylab = "Emissions (in tons)",xlab = "Year")

```
# Course Project 2
Fine particulate matter (PM2.5) is an ambient air pollutant for which there is strong evidence that it is harmful to human health. In the United States, the Environmental Protection Agency (EPA) is tasked with setting national ambient air quality standards for fine PM and for tracking the emissions of this pollutant into the atmosphere. Approximatly every 3 years, the EPA releases its database on emissions of PM2.5. This database is known as the National Emissions Inventory (NEI). You can read more information about the NEI at the [EPA National Emissions Inventory web site](https://www3.epa.gov/ttn/chief/eiinformation.html).
For each year and for each type of PM source, the NEI records how many tons of PM2.5 were emitted from that source over the course of the entire year. The data that you will use for this assignment are for 1999, 2002, 2005, and 2008.
> Review criteria

For each question
1. Does the plot appear to address the question being asked?
2. Is the submitted R code appropriate for construction of the submitted plot?
> Data

The data for this assignment are available from the course web site as a single zip file:
[Data for Peer Assessment  29Mb](https://d396qusza40orc.cloudfront.net/exdata%2Fdata%2FNEI_data.zip)
The zip file contains two files:

PM2.5 Emissions Data (summarySCC_PM25.rds): This file contains a data frame with all of the PM2.5 emissions data for 1999, 2002, 2005, and 2008. For each year, the table contains number of tons of PM2.5 emitted from a specific type of source for the entire year. Here are the first few rows.
```{r }
head(NEI)
```

